Polynomial representations of rational Cherednik algebras of type $A$ in positive characteristic $p \mid n$

### 2015-05-07 ci.tex
fixed r=1 argument

If $r=1$, then $g(z)= \left(\sum_{k=0}^{p-1} (-1)^k \binom{c}{k} y_0^kz^k\right)^n$ and $f_0(z)=\frac{1}{1-y_0z}\left(\sum_{k=0}^{p-1} (-1)^k \binom{c}{k} y_0^kz^k\right)^n$. We note that $[z^p]f_0(z)=\sum_{k=0}^p y_0^{p-k}[z^k]g(z)$. For $k=1,\dots,p-1$ we note that the term $[z^k]g(z)$ is a linear combination of terms of the form $\binom{n}{\ell_1}\binom{n-\ell_1}{\ell_2}\dots\binom{n-\ell_1-\dots-\ell_{s-1}}{\ell_s}(-1)^k\binom{c}{k_1}^{\ell_1}\dots\binom{c}{k_s}^{\ell_s}y_0^k$ where $\ell_1,\dots,\ell_s$ are positive integers and $k_1,\dots,k_s$ are distinct positive integers with $\sum \ell_ik_i=k$ - this represents the product of $\ell_i$ terms $ (-1)^{k_i}\binom{c}{k_i} y_0^{k_i} z^{k_i}$.

. In particular this means that $0 < \ell_1 < p$, so $\binom{n}{\ell_1}$ is $0$ in characteristic $p$, so all of these terms are $0$. This means that $[z^p]f_0(z)=y_0^p[z^0]g(z)+[z^p]g(z)=y_0^p+[z^p]g(z)$. Note that $[z^p]g(z)$ is the sum of terms of the form $\binom{n}{\ell_1}\binom{n-\ell_1}{\ell_2}\dots\binom{n-\ell_{s-1}}{\ell_s}(-1)^k\binom{c}{k_1}\dots\binom{c}{k_s}y_0^k$ where $\ell_1,\dots,\ell_s$ are positive integers and $k_1,\dots,k_s$ are distinct positive integers with $\sum \ell_ik_i=p$; this term is $0$ unless $\ell_1=p$, so $[z^p]g(z)=\binom{n}{p}(-1)^p\binom{c}{1}^py_0^p=\binom{n}{p}(-c)^py_0^p$. Therefore $[z^p]f_0(z)=\left(1+\binom{n}{p}(-c)^p\right)y_0^p$; if this is $0$ but $y_0 \ne 0$, then $1+\binom{n}{p}(-c)^p=0$; this is false since $c$ is generic. Therefore $y_0=0$. This completes the case $r=1$. We now assume $r>1$.

>>>>

If $r=1$, then $g(z)= \left(\sum_{k=0}^{p-1} (-1)^k \binom{c}{k} y_0^kz^k\right)^n$ and $f_0(z)=\frac{1}{1-y_0z}\left(\sum_{k=0}^{p-1} (-1)^k \binom{c}{k} y_0^kz^k\right)^n$. We note that $[z^p]f_0(z)=\sum_{k=0}^p y_0^{p-k}[z^k]g(z)$. For $k=1,\dots,p$ we note that the term $[z^k]g(z)$ is a linear combination of terms of the form $\binom{n}{\ell_1}\binom{n-\ell_1}{\ell_2}\dots\binom{n-\ell_1-\dots-\ell_{s-1}}{\ell_s}(-1)^k\binom{c}{k_1}^{\ell_1}\dots\binom{c}{k_s}^{\ell_s}y_0^k$ where $\ell_1\ge\dots\ge\ell_s$ are positive integers and $k_1,\dots,k_s$ are distinct positive integers with $\sum \ell_ik_i=k$ - this represents the product of $\ell_i$ terms $ (-1)^{k_i}\binom{c}{k_i} y_0^{k_i} z^{k_i}$. In particular the coefficients of these terms are polynomials in $c$ that are divisible by $c$. Therefore $[z^p]f_0(z)=y_0^p+cs(c )y_0^p$ where $s(c )$ is a polynomial in $c$. If this is $0$ but $y_0^p$ is nonzero, then $cs(c )+1$ is $0$ as a polynomial of $c$ since $c$ is generic; this is false since it has constant term $1$. Therefore $y_0=0$. This completes the case $r=1$. We now assume $r>1$.
